---
title: "Part 1"
author: "Isaac Moore"
date: "May 17, 2016"
output: html_document
---
### Number 1
In part one we will examine the Central Limit Therom (CLT) by simulating 1000 means of 40 random exponentials using the ```{r} rexp() ``` command.  
**Initalize the data to be used for the analysis.**
```{r setup, include=TRUE, echo=TRUE}
set.seed(1987)
lambda <- 0.2
sd <- 1/lambda
sims <- 1000
n <- 40
data <- NULL
```
**Comparing the theoretical mean to the actual mean of the simulated data.**
```{r}
for(i in 1 : sims){
data <- c(data, mean(rexp(n, lambda)))
}
theoretical_mean <- 1/lambda 
theoretical_mean
actual_mean <- mean(data)
actual_mean
```

We can see there is a difference of 0.006829905 between the theoretical mean and the actual mean.  
**Plotting the data**
```{r}
hist(data, breaks = 'Sturges')
abline (v = theoretical_mean, col = 'red')
abline(v = actual_mean, col = 'green')
legend('topright', pch = 19, col = c('red', 'green'), legend = c('Theoretical Mean', 'Actual Mean'))
```

We can see that the actual mean mean is very close to the theoretical mean - the number of simulations we increase, closer the actual mean will get to the theoretical mean.  

### Number 2  
**Comparing the variance of the actual simulated data to the theoretical variance.**  
```{r}
actual_std_dev <- sd(data)
actual_variance <- actual_std_dev^2
actual_variance
theoretical_std_dev <- (1/lambda)/sqrt(n)
theoretical_variance <- theoretical_std_dev^2
theoretical_variance
```
We can see that there is a large difference between the theoretical variance and the actual variance - 0.02252434  

### Number 3  
**Comparing the simulated distribution to the normal distribution.**  
```{r}
xfit <- seq(min(data), max(data), length=1000)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda)/sqrt(n))
hist(data, breaks = 'Sturges', probability = T)
lines(xfit, yfit, type ='l', lwd = 1, col = 'red')
legend('topright', pch = 19, col = c('red'), legend = c('Normal Distribution'))
```

We can see that the distribution is very close to being normally distributed. The number of simulations we increase, the closer the distribution will get to being normally distributted. 