---
title: "Part 2"
author: "Isaac Moore"
date: "May 17, 2016"
output: pdf_document
---
In this analysis we will look at the "ToothGrowth" dataset which is "The Effect of Vitamin C on Tooth Growth in Guinea Pigs"  
Initialize libraries into R.
```{r setup, include=TRUE, echo=TRUE}
library('dplyr')
library('ggplot2')
```

### Number 1  
**Load the data into R**
```{r}
data('ToothGrowth')
tooth_growth <- tbl_df(ToothGrowth)
tooth_growth
```
### Number 2  
**Exploratory data analysis and summary of the data**  
60 guinea pigs were doses of vitamin C in one of three doeses - 0.5mg, 1mg, or 2mg / day. There were two delivery methods orange juice (coded as 'OJ') or asorbic acid(coded as 'VC').
```{r}
oj <- tooth_growth %>% filter(tooth_growth$supp == 'OJ')
summary(oj$len)
vc <- tooth_growth %>% filter(tooth_growth$supp == 'VC')
summary(vc$len)
```
We can see based off of the means of both summaries that OJ yileds greater results.  
Next, Lets take a look at the mean for OJ and VC at each dose.  
*Orange Juice (OJ)*
```{r}
oj_dose_lens <- tooth_growth %>% filter(tooth_growth$supp == 'OJ') %>%
        group_by(dose) %>%
        summarise(oj_mean_len = mean(len))
oj_dose_lens
```
*Asorbic Acid (VC)*
```{r}
vc_dose_lens <- tooth_growth %>% filter(tooth_growth$supp == 'VC') %>%
        group_by(dose) %>%
        summarise(vc_mean_len = mean(len))
vc_dose_lens
```
*Plot showing the data*
```{r}
plot <- ggplot(tooth_growth, aes(supp, len))+geom_point()
plot + facet_grid(.~dose)+
        labs(title='Supplements at each dose', y='Tooth Length',x='Supplement')
```

We can see from the analysis performed above that at doses 0.5mg and 1mg orange juice outperforms asorbic acid, but asorbic outperforms orange juice at 2mg, but is more disperse.   

### Number 3
**Welch Two Sample t-test**  
t-test for orange juice and asorbic acid.
```{r}
t.test(oj$len, vc$len, paired = FALSE, var.equal = FALSE)
```
*Testing the disperse 2mg dose.*  
Initalize the data to perform the test.
```{r}
oj_2 <- filter(tooth_growth, dose == 2.0)
oj_2 <- filter(oj_2, supp == "OJ")
vc_2 <- filter(tooth_growth, dose == 2.0)
vc_2 <- filter(vc_2, supp == "VC")
```
t-test
```{r}
t.test(oj_2$len, vc_2$len, paired = FALSE, var.equal = FALSE)
```